Modern Graph Generators: A Survey

### 2018-11-27 generators_GraphDatabases.tex
Correction of XGDBench

\paragraph{XGDBench} XGDBench~\cite{Dayarathna:2014:GDB:2676904.2676939} is an extensible graph database benchmarking platform for cloud-based systems. Its intent is to automate
the process of graph database benchmarking in the cloud by focusing on a graph database application for social networking services. It extends the Yahoo! Cloud Multiplicative Attribute (MAG) Graph Serving Benchmark (YCSB)~\cite{Cooper:2010:BCS:1807128.1807152} and \iffalse consists of of a workload generator client and\fi provides a package of standard workloads that cover interesting parts of the performance space.
\iffalse In particular, the workload generator of YCSB supports definition of new workload types.\fi In particular, the workload of XGDBench involves basic operations such as read / insert / update / delete an attribute, loading of the list of neighbors and BFS traversal. Using the generators, 7 workloads are created, such as update heavy, read mostly, short range scan, traverse heavy etc.
The data model of XGDBench is a simplified version of the Multiplicative Attribute Graph (MAG)~\cite{Kim2010} model, a synthetic graph model for attribute graphs which models the interactions between the network structure and the node attributes.
The generated graphs are thus in MAG format, with power-law degree distribution closely simulating real-world social networks.
The simplified MAG algorithm accepts the number of vertices of the generated graph, the number of attributes per vertex, a threshold value for random initialization of attributes, an edge affinity threshold value that determines whether there is an edge between two vertices, and an affinity matrix. \iffalse It has been proven that MAG generates graphs with both analytically tractable and statistically interesting properties.\fi A multi-threaded version of the graph generator that generates large graphs on multi-core systems faster was implemented too.

>>>>

\paragraph{XGDBench} XGDBench~\cite{Dayarathna:2014:GDB:2676904.2676939} is an extensible  benchmarking platform for graph databases used in cloud-based systems. Its intent is to automate
the process of graph database benchmarking in the cloud by focusing on the domain social networking services. It extends the Yahoo! Cloud Multiplicative Attribute (MAG) Graph Serving Benchmark (YCSB)~\cite{Cooper:2010:BCS:1807128.1807152} and provides a set of standard workloads representing various performance issues. In particular, the workload of XGDBench involves basic operations such as read / insert / update / delete an attribute, loading of the list of neighbors and BFS traversal. Using the generators, 7 workloads are created, such as update heavy, read mostly, short range scan, traverse heavy etc.
The data model of XGDBench is a simplified version of the Multiplicative Attribute Graph (MAG)~\cite{Kim2010} model, a synthetic graph model which models the interactions between  node attributes and  graph structure.
The generated graphs are thus in MAG format, with power-law degree distribution closely simulating real-world social networks.
The simplified MAG algorithm accepts the required number of nodes, the number of attributes per each node, a threshold value for random attribute initialization, an edge affinity threshold determining existence of an edge between two nodes, and an affinity matrix. \iffalse It has been proven that MAG generates graphs with both analytically tractable and statistically interesting properties.\fi 
Large graphs can be generated on multi-core systems by a multi-threaded version of the  generator.
